Model matters with restricted Boltzmann machines

### 2017-01-18 presentations/uva/slides.Rmd
cleanup language surrounding instability

- fail to generate data with realistic variability and thus an unsatisfactory conceptualization of the data generation process [@li2014biclustering] 
- exhibit instability in the parameter space [@szegedy2013intriguing; @nguyen2014deep]

>>>>

- fail to generate data with realistic variability and thus an unsatisfactory conceptualization of the data generation process [@li2014biclustering] 
- exhibit model instability (over-sensitivity) [@szegedy2013intriguing; @nguyen2014deep]
